Subset coercions in \Coq

### 2006-05-01 papers/article/main.tex
Update outline

The really interesting rules are \irule{SubSub} and
\irule{SubProof}. The first one allows to use an object of a subset type
as an object of its support type. The latter allows (maybe abusively) to
consider an object of any type as an object of any subset based on
it. By the assumption on the input types of the judgment, we now that $P$
is well-typed, but we do not care about the proof.

@@

\begin{paragraph}{Results}

\end{paragraph}

\begin{paragraph}{Algorithmic typing}
\end{paragraph}

>>>>

The really interesting rules are \irule{SubSub} and
\irule{SubProof}. The first one allows to use an object of a subset type
as an object of its support type. The latter allows (maybe abusively) to
consider an object of any type as an object of any subset based on
it. By the assumption on the input types of the judgment, we know that $P$
is well-typed, but we do not care about the proof.

@@

\begin{paragraph}{Results}
  - Weakening
  - Substitution
\end{paragraph}

\subsubsection{Algorithmic typing}
  - Standard transformation for subtyping
  - mu
  - Elimination of transitivity
  - Soundness and completeness
